Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-07 Paper.tex
noindent

% images in cancer research, histopathology --> digital pathology
Today, large sequencing approaches build the main body of cancer
research programs and they have revolutionized our understanding of
the molecular basis of cancer. In clinical practice however,
molecular profiling is paralleled with the more traditional
(and mostly manual) analysis of stained histological tumor
sections. With the avent of digital pathology, i.e. the scanning and
digital storage of diseased tissue sections, it is now possible to
build tools for the quantitative and automatic analysis of these
complex and informative image data. Indeed, this is a very promising
approach for several reasons: image based approaches
provide us with spatial information that is absent in genomic,
transcriptomic and epigenetic studies of cancer. In addition they
allow analysis of individual cells, such that it is possible to study
cellular heterogeneity. Cellular heterogeneity has been acknowledged
to be of major importance in cancer research and treatment. Also, it
is possible to analyze cells in terms of morphology and phenotype,
which brings in a complementary piece of functionally relevant
information.

>>>>

% images in cancer research, histopathology --> digital pathology
\noindent Today, large sequencing approaches build the main body of cancer
research programs and they have revolutionized our understanding of
the molecular basis of cancer. In clinical practice however,
molecular profiling is paralleled with the more traditional
(and mostly manual) analysis of stained histological tumor
sections. With the avent of digital pathology, i.e. the scanning and
digital storage of diseased tissue sections, it is now possible to
build tools for the quantitative and automatic analysis of these
complex and informative image data. Indeed, this is a very promising
approach for several reasons: image based approaches
provide us with spatial information that is absent in genomic,
transcriptomic and epigenetic studies of cancer. In addition they
allow analysis of individual cells, such that it is possible to study
cellular heterogeneity. Cellular heterogeneity has been acknowledged
to be of major importance in cancer research and treatment. Also, it
is possible to analyze cells in terms of morphology and phenotype,
which brings in a complementary piece of functionally relevant
information.
